---
title: CV
name: Caitie
surname: Reza
position: "Masters Student"
address: "Bren School of Environmental Science & Managment, University of California Santa Barbara"
phone: +1 661 666 1356
www: 
email: "caitlinreza@ucsb.edu"
github: https://github.com/CaitieReza/
linkedin: https://www.linkedin.com/in/caitie-reza-50b8a7115/
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::markdowncv:
    theme: davewhipp
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

## Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Masters of Environmental Science and Management", "2020-22", "The Bren School, UCSB", "Santa Barbara, California",
  "Bachelors in Zoology", "2019", "Michigan State University", "East Lansing, Michigan",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

## Research Experience

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

## Publications

```{r}

```


1. Aminpor, P., Gray, S., **Reza, C.**, Scyphers, S., Grabowski, J., Murphy, B., and Baltaxe, D., Harnessing Collective
Intelligence for Conservation, Frontiers in Ecology and the Environment (2020)

2. Schwermer, H., Aminpor, P., **Reza, C.**, Funk, S., Möllmann, C., and Gray, S. Modeling and Understanding
Biocultural Variations, Conservation Science and Practice (In Review)
