---
title: "Exploring Species-Specific Traits with Binary Logistic Regression"
description: |
  Two Species of Palmetto Trees Walk Into an .rmd file
author:
  - name: Caitie Reza
date: 01-20-2021
output:
    distill::distill_article:
    self_contained: false
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(GGally)
library(broom)
library(jtools)
library(beeswarm)
library(ggbeeswarm)
library(stargazer)
library(GGally)
library(kableExtra)
library(janitor)
library(patchwork)
library(tibble)
```

### Summary 

This report utilizes data from the Archbold Biological Station in South-Central Florida (see citation below) to explore the phenology and assess the classification of two plant species of Palmetto trees: *Serenoa repens* and *Sabal etonia*.  Here, we use binary logistic regression to analyze the relationship between the species and an array of dependent variables.  


###### Data: Abrahamson, W.G. 2019. Survival, growth and biomass estimates of two dominant palmetto species of south-central Florida from 1981 - 2017, ongoing at 5-year intervals ver 1. Environmental Data Initiative. 

```{r, echo = TRUE, warning = FALSE, message = FALSE}
# 1. Read in Data
palmetto <- read_csv("palmetto.csv", 
  col_types = cols(.default = "c")) %>%  #convert all to character
    mutate(height = as.numeric(height)) %>% # convert our explanatory variables to numeric
  mutate(length = as.numeric(length)) %>% 
  mutate(width = as.numeric(width)) %>% 
  mutate(green_lvs = as.numeric(green_lvs))


```

#### **Figures 1-3**: Visualizing Phenotypic Differences Between Palmetto Species 

```{r, echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center"}
#  Visualize relationships (or lack thereof) between my predictor variables to see if I spot any patterns

ggplot(data = palmetto, aes(x = green_lvs, y = height)) +
         geom_point(aes(color = species)) +
         facet_wrap(~species, scales = "free") +
  labs(x = "Number of New Green Leaves", y = "Plant Height (cm)",
       color = "Species")
  


```
**Figure 1.** shows the relationship between green leaf counts and plant height (cm) in 2 unidentified species of palmetto tree. Note the different scale between x axes (number of green leaves) and y axes (plant height). 

- Both species exhibit a relatively positive relationship between green leaf counts and plant height.


```{r, echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center"}

ggplot(data = palmetto, aes(x = species, y = green_lvs, na.rm = TRUE)) +
  geom_jitter(aes(color = species)) +
  labs(x = "Species", y = "Number of New Green Leaves",
       color = "Species") +
  theme(legend.position = "none") 

```

**Figure 2.** demonstrates the number of green leaves on Palmetto plants of Species 1 and 2.

- Based on the count data, Species 1 plants tend to have more new, green leaves as compared to Species 2.

```{r, echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center"}

ggplot(data = palmetto, aes(x = length, y = width)) +
  geom_point(aes(color = species)) +
  facet_wrap(~species) +
  labs(x= "Canopy Length (cm)", y = "Canopy Width (cm)",
       color = "Species")

```


**Figure 3.** shows the relationship between canopy length (cm) and canopy width (cm) measured for both Palmetto species.

- At first glance, there seems to be a positive correlation between canopy length and canopy width in both species.  



### Binary Logistic Regression Model

<div align="center"> 
```{r, echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center", r, results = 'asis'}

# Binary Logistic Regression

# Make subset with just our predictor + explanatory variables

palm_sub <- palmetto %>% 
  select(species, height:green_lvs) %>% 
  mutate(species = as.factor(species)) # make species a factor

# Check the levels in the console 
# levels(palm_sub$species)

# Perform BLR

palm_blr <- glm(species ~ height + length + width + green_lvs, 
                            data = palm_sub, 
                            family = "binomial")
# View my model in the console 'view(palm_blr)'


# View model summary in the console 'summary(palm_blr)'


# Make it tidy
blr_tidy <- broom::tidy(palm_blr)

blr_tidy

# Make finalized table Containing Binary Logistic Regression Model information

stargazer(palm_blr, type = "html",
          title = "**Table 1.** Predicting Species using Palmetto height, canopy length, canopy width, and Leaf Count",
          covariate.labels = c("Height", "Canopy Length", "Canopy Width",
                               "Number of Green Leaves"),
          dep.var.caption  = "Dependent Variable:",
          dep.var.labels   = "Species")

```
</div> 

### Classifying Palmetto Species 


```{r, echo = TRUE, warning = FALSE, message = FALSE}

# Find probability of association between explatory variables + species
blr_fitted <- palm_blr %>% 
  broom::augment(type.predict = "response") %>% 
   mutate(predicted_species = case_when(
     .fitted >= .5 ~ "2",
     .fitted < .5 ~ "1")) %>% 
  mutate(species_name = case_when( # Replace 1's and 2's in species column with species names, for clarity and to make them characters
    predicted_species %in% 1 ~ "one",
    predicted_species %in% 2 ~ "two"))


# Visualize for different explanatory variables, store as object so it doesn't come up in html

apple <- ggplot(data = blr_fitted, aes(x = green_lvs, y = .fitted)) +
  geom_point(aes(color = species)) +
  geom_smooth(aes(color = species), se = FALSE)


```




    
```{r, echo = TRUE, warning = FALSE, message = FALSE}

# Make subset of blr_fitted
fitted_sub <- blr_fitted %>% 
  select(species, .fitted) %>% 
  mutate(predicted_species = case_when(
    .fitted >= .5 ~ "2",
    .fitted < .5 ~ "1")) %>% 
  mutate(outcome = case_when(
    species == predicted_species ~ "Correct",
    species != predicted_species ~ "Incorrect")) %>% 
  mutate(species = as.numeric(species)) %>% 
  mutate(predicted_species = as.numeric(predicted_species)) %>% 
  group_by(species, outcome) %>% 
  count(outcome) %>% 
  pivot_wider(names_from = outcome,
              values_from = n) %>% 
  mutate(species = case_when(
    species %in% 1 ~ "Serenoa repens (Species 1)",
    species %in% 2 ~ "Sabal etonia (Species 2)")) %>% 
      column_to_rownames(var = "species")


# Add a column showing percent (thanks google)

fitted_sub['% Correct'] = fitted_sub['Correct'] / (fitted_sub['Incorrect'] + fitted_sub['Correct']) * 100


```




**Table 2.** shows the number and proportion of plants classified correctly for each species. Here, "Classified Correctly" means that the individual S. repens surveyed was correctly identified as S. repens 
```{r, echo = TRUE, warning = FALSE, message = FALSE, fig.align = "center"}

# Make Pretty using Kable and view!
fitted_sub %>% 
  kable(digits = 2) %>% 
   kable_styling(bootstrap_options = "striped", full_width = FALSE)

```
